Concurrent Programming with Harmony

### 2020-07-28 book/paper.tex
Latest

  description={is a process that is waiting on a low-level synchronization primitive
    and cannot terminate without the help of another process.
      For example, a process that is waiting for a spinlock to become available}

@@

Harmony can report a variety of failure types:
\begin{itemize}
\item \texttt{Safety violation}: this means something went wrong with
at least one of the executions of the program that it tried.  This
can include a failing assertion, divide by zero, using an uninitialized
or non-existent variable, dividing a set by an integer, and so on.
It also includes certain infinite loops.
Harmony will print at trace of the shortest bad execution that it found.
\item \texttt{Non-terminating States}: Harmony found one or more states
from which there does not exist an execution such that all processes
terminate.  Harmony will not only print the non-terminating state with
the shortest trace, but also the list of processes that are running
at that state, along with their name tags and program counters.
\item \texttt{Stopped States}: Similar to non-terminating states,
these are states in which some processes are left that cannot
terminate.  \autoref{ch:synch} will explain what it means for
a process to be stopped.
\end{itemize}

@@

We call a process \emph{blocked}
\index{blocked process}%
in a state if the process is waiting on a low-level synchronization
variable and cannot terminate without the help of another process.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.

@@

A context is considered \emph{blocked}
\index{blocked process}%
if there does not exist a
sequence instructions that the process can execute by itself
that leads to its termination.

@@

Executing a Harmony program results in a graph where the nodes are Harmony
states and the edges are macro steps.
When a state is \texttt{choosing}, the edges from that state are
by a single context, one for each choice.  If not, the edges from
the state are one per context.
A terminating state is a state with an empty context bag or a state
where all contexts are blocked.

>>>>

  description={is a process that cannot change the state unless another
    process changes the state first.  For example, a process that is waiting
    for a lock to become available.}

@@

Harmony can report a variety of failure types:
\begin{itemize}
\item \texttt{Safety violation}: this means something went wrong with
at least one of the executions of the program that it tried.  This
can include a failing assertion, divide by zero, using an uninitialized
or non-existent variable, dividing a set by an integer, and so on.
It also includes certain infinite loops.
Harmony will print at trace of the shortest bad execution that it found.
\item \texttt{Non-terminating States}: Harmony found one or more states
from which there does not exist an execution such that all processes
terminate.  Harmony will not only print the non-terminating state with
the shortest trace, but also the list of processes
at that state, along with their name tags and program counters.
\item \texttt{Stopped States}: Similar to non-terminating states,
these are states in which some processes are left that cannot
terminate.  \autoref{ch:synch} will explain what it means for
a process to be stopped.
\end{itemize}

@@

We call a process \emph{blocked}
\index{blocked process}%
if the process can only change the state if another process changes
the state first.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.

@@

@@

Executing a Harmony program results in a graph where the nodes are Harmony
states and the edges are macro steps.
When a state is \texttt{choosing}, the edges from that state are
by a single context, one for each choice.  If not, the edges from
the state are one per context.
